\documentclass[12]{article}
\begin{document}
\begin{title}
\huge{CONCEPT PAPER }
\end{title}
\maketitle
\author{TAGUYISIZA YAHAYA	14/U/15104/PS	214009743}
\section{Introduction}
Government sponsorship this happens when a student is sponsored by government to study at the university. Private sponsorship here a student is sponsored by an individual that is his or her parent, a guardian, an NGO, or any other individual or organization besides the government. A student to be admitted on government sponsorship, he or she should have performed very well in his or her A level, O level, Primary. Even some disabled students are admitted on merit depending on their performance. 
\section{Background of the prpoblem}
Admission at university is based on student’s performance at their secondary schools at most their A level results. That is a student is at least required to have scored two points and above. After a student scores two points and above they get sponsors for their studies at university. The sponsors can either be government or private. The government of Uganda sponsors students for their studies at the university. These universities include Makerere University, Kyambogo University, Gulu University, Muni University, Mbarara University. A student to be admitted on government sponsorship, he or she should have performed very well in his or her A level, O level, Primary. Even some disabled students are admitted on merit depending on their performance. Schools try their best to teach and provide the best facilities to their students so that they perform to their best to qualify for the government sponsorship at university. Here students are given forms to fill to apply for these sponsorships. All those students who fall out on government sponsorship, are privately sponsored for their admission to the university.
Privately sponsored students are in different kinds that is those sponsored by their own parents, those sponsored by their guardians, those sponsored by NGOs, those sponsored by other individuals and organization. 

\section{Problem statement}
This research is about knowing the school that dominates the government                                                                                                                                                                                                              admissions at CIT and this will help school know their levels of government admissions at College of Informatics Technology (CIT) thus checking what to improve so that they increase of government admission at CIT.   
\section{Objectives}
\subsection{Main objectives}
To get to know which secondary school admits most student on government at CIT.
\subsection{Specific objectives}
To gather data to be used in the research.
To analyze the gathered information.
To come up with the final report.

\section{Research scope}
My research  is to be carried about randomly amongst students admitted at CIT. At this college these are the courses by students and these include; BSc.CSC, BSc.SE, BSc. IS, BSc.IT. These courses are computer and technology related.
\section{Research significance}
This research is to benefit secondary school to know their levels of admission of students on government. So that their can improve or maintain their performance for their student to be admitted at the college of computing and technology.
\end{document}
