\documentclass[12]{article}

\begin{document}

\title{REPORT SHOW THE SCHOOL DOMINATING GOVERNMENT ADMISSION AT CIT}
\maketitle
\author{TAGUYISIZA YAHAYA   14/U/15104/PS    214009743}
\newpage
\section{Acknowledgement}
I would like to thank my research methodology lecturer Mr Ernest Mwebaze, CIT students who help me with their information as I was collecting data.
\section{Introduction}
\subsection{Background}
Admission at university is based on student’s performance at their secondary schools at most their A level results. That is a student is at least required to have scored two points and above. After a student scores two points and above they get sponsors for their studies at university. The sponsors can either be government or private. The government of Uganda sponsors students for their studies at the university. These universities include Makerere university, Kyambogo university, Gulu university, Muni university, Mbarara university. A student to be admitted on government sponsorship, he or she should have performed very well in his or her A level, O level, Primary. Even some disabled students are admitted on merit depending on their performance. Schools try their best to teach and provide the best facilities to their students so that they perform to their best to qualify for the government sponsorship at university. Here students are given forms to fill to apply for these sponsorships. All those students who fall out on government sponsorship, are privately sponsored for their admission to the university.
Privately sponsored students are in different kinds that is those sponsored by their own parents, those sponsored by their guardians, those sponsored by NGOs, those sponsored by other individuals

\subsection{Objectives}
\subsubsection{Main Objectives}
To get to know which secondary school admits most student on government at CIT.
\subsubsection{Specific Objectives}
To gather data to be used in the research.
To analyze the gathered information.
To come up with the final report.

\section{Methodology}
\subsection{Research question}
I used these questions for my research and their include:
What is your first name?
What is your last name?
What is your student number?
What is your registration number?
State  your academic year?
State the course you are pursuing?
What is your former secondary school?
In which district is your former secondary school?
Who is your sponsor?
\subsection{Research design}
I use ODK as my research design which is an on-line tool used for collecting data.  
Method used to answer the question
\subsection{Data collection}
I collected this data using ODK collect application. The application helps you to generate forms for filling in to get the information required. The individuals whose information I got I met them face to face and I requested them to help me fill the forms. I conducted my research in English. 
\subsection{Data analysis}
ODK build is the tool that I used to create an electronic form for data collection. This form is accessed using the ODK collect application which is enter the gathered information into the computer. This information is stored and analyzed using ODK aggregate.

\subsection{Limitation}
During my research I faced limitations such as;
Since its towards examinations, students were had to find so that I get information from them.
Time was short for me to conduct the research.
Students being in tests so students were always busy so it was hard to get information from them.

\end{document}
